Improving the Replicability of Psychological Science Through Pedagogy

### 2017-07-26 paper/paper.Rmd
Small edits + costs section

In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants (see Fig. 1). 
In the second week of the course, students wrote a brief proposal selecting their replication targets, which were reviewed for feasibility and concreteness. 
After their selection was approved, students proceeded to write the methods section of the @osc2015 replication report template. 
This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template). 
At the same time, students worked on an experiment "mock-up": a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design. 
Upon reviewing the completed methods and mockup, the teaching staff gave thorough feedback and suggested changes to be made before beginning any data collection.

@@

All of the 15 students in the class completed projects (two with extensions going beyond the class period). Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations, and materials to the final product. (In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review. We included this project in the final analysis.)

@@

Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design. Without a central focus on the replication project, students will not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.

@@

Still, collecting sufficiently large samples through AMT may strain financial resources. Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g., through teaching grants or departmental support), other populations may be more feasible and appropriate. For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.

Cost considerations also enter decisions about determining appropriate sample sizes, a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But it may not be feasible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies, but be unnecessary for studies that were initially large and/or adequately powered.

As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature. Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.

@@

All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of a single unified document that would become their final report. This method of writing allows students to easily share their cumulative work to date with instructors via a hyperlink, facilitating review of exposition, results, and code together in one location^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].

@@

`r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value at $p < .05$. 
<!-- The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.  -->

>>>>

In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants (see Fig. 1). 
In the second week of the course, students wrote brief proposals selecting their replication targets, which were reviewed for feasibility and concreteness. 
After their selection was approved, students proceeded to write the methods section of the @osc2015 replication report template. 
This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template). 
At the same time, students worked on an experiment "mock-up": a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design. 
Upon reviewing the completed methods and mockup, the teaching staff gave thorough feedback and suggested changes to be made before beginning any data collection.

@@

All of the 15 students in the class completed projects (two with extensions going beyond the class period). Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would not replicate.] The remaining 11 students contributed code, data, registrations, and materials to the final product. (In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review. We included this project in the final analysis.)

@@

Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design. Without a central focus on the replication project, students would likely not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.

@@

Depending on the course design and total funds allocated to the course (if any), populations other than AMT may be more feasible and appropriate.  We recommend instructors explore funding opportunities through teaching grants or departmental support, but note that a replication course without funding would be possible. For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.

Cost considerations must also enter into decisions about adequate sample sizes, which has been a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But it may not be feasible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies, but be unnecessary for studies that were initially large and/or adequately powered.

As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples. Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature. Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.

@@

All our studies were coded in JavaScript, HTML, and CSS to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of a single unified document that would become their final report. This method of writing allows students to easily share their cumulative work to date with instructors via a hyperlink, facilitating review of exposition, results, and code together in one location^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].

@@

Of the `r nrow(d)` studies, `r sum(d$rep_p_value_05)` (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value at $p < .05$. 
<!-- The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.  -->
